---
title: "Budget Data - Himachal Pradesh"
author: "preethi"
date: "1/4/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Week 3 - Developing Data Products - Test 1

- For the third week, the instructions were to create a web page presentation using R Markdown that features a plot created with Plotly.
- For this assignement, I have created a graph with Plotly depicting distric-wise health care expenditure on the x-axis, number of primary health care centres in the y-axis and population in district as the size of the circles

## District-wise public health expenditure and number of hospitals in Himachal Pradesh

```{r district_data, message=FALSE, warning=FALSE, echo = FALSE, fig.width=14, fig.height=10}
library(ggplot2)
library(plotly)
district_exp <- read.csv("C:/Users/Preethi's Laptop/Documents/R/datascience_coursera_main/HP expenditure/HP-expenditure/HP budet and expenditure data/districtwise_spend.csv", header = TRUE)
district_exp$district <- district_exp$ï..district


plot3 <- ggplot (data = district_exp, 
                 aes(x = Public_Health_Expenditure,y=Number_PHC, fill = district, size=Population))+
                  geom_point(alpha = 0.5, shape = 21)+scale_x_continuous(labels = scales::comma)+  
                  scale_size(range = c(.1, 24), name="Population")+
                  ggtitle("Figure 1: HP - District-wise public health expenditure") +
                  theme_bw()+
                  xlab("District wise healthcare expenditure in Rs") + ylab("Number of Primary Health Care Centres")
ggplotly (plot3)
```

## Thank you
