---
title: "Pitch_Application - Week 4"
author: "preethi"
date: "1/13/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Shiny Application - Week 4 - Developing Data Products

This is a tiny pitch deck for the web application created by Preethi Govindarajan for the developing data products course

## Slide with Bullets

- The purpose of this application is to observe time related trends in sector-wise budget data in different Indian States

- There are two drop downs for State and Sector 

- Below is a simple graph for sector wise expenditure in the state of Assam

```{r comment=FALSE,echo=FALSE, message=FALSE, warning=FALSE}

library(reshape2)
library(ggplot2)
library(tidyr)
timeseries <- read.csv("sector-specific-state-aggregate-expenditure-2013-14-actuals-to-2016-17-budget-estimates.csv", header = TRUE)
timeseries  <- timeseries[!grepl("Revenue Expenditure as % of Total Sector Expenditure", timeseries$Indicators),]
timeseries  <- timeseries[!grepl("Per Capita Expenditure on Sector", timeseries$Indicators),] 
timeseries <- timeseries[!grepl("Total Sector Expenditure as % of State Budget", timeseries$Indicators),]
timeseries  <- timeseries[!grepl("Capital Expenditure", timeseries$Indicators),]
timeseries <- timeseries[,c("Sectors",colnames(timeseries)[grep("Assam", colnames(timeseries))])]
timeseries <- timeseries[,c("Sectors",colnames(timeseries)[grep("Budget", colnames(timeseries))])]
timeseries$Sectors <- substring(timeseries$Sectors, 4)
timeseries_melt <- melt(timeseries)
timeseries_melt<- separate(data = timeseries_melt, col = variable, into = c("State", "Year1, Year2", "type1","type2"), sep = "\\.")
timeseries_melt$year <- paste(timeseries_melt$`Year1, Year2`,timeseries_melt$type1,sep="-")
timeseries_melt[,c("Year1, Year2", "type1", "type2")] <- list(NULL)

##timeseries_melt <- unite(data = timeseries_melt, col = "Sectors", Sectors:Indicators, remove = TRUE)
plot1 <- ggplot (data = timeseries_melt,aes(x = year, y=value, color = Sectors, group = Sectors)) + 
  geom_line(size=1)+ geom_point(size=3)+scale_y_continuous(labels = scales::comma)+  
  ggtitle("Figure 1: Plot of Sectorwise budget in Assam from 2014 to 2018") + 
  xlab("year") + ylab("Budget in lakhs")+
  guides(size = FALSE)+
  theme(plot.margin = margin(2,.8,2,.8, "cm"), plot.background = element_rect(fill = "darkgrey"))

print(plot1)

```

## Other Documents
- The documentation neccesary for this is found in [Help_document.rmd](https://github.com/preethical/Shiny-tryouts)  

-  The global, server and ui. R files are found   [here](https://github.com/preethical/Shiny-tryouts/tree/master/Shiny_app_week4)  

-  All the other weeks assignments are found [here](https://preethical.github.io/Shiny-tryouts/)   

-  Application link [here](https://preethical.shinyapps.io/Week4_Programming_Assignment/)  

## Thank you for your time
